Figures

### 2024-05-24 figures/figures.Rmd
linting

```{r, echo=FALSE}
if(dir.exists("../scripts")){
    shim <- "../"
    source("../scripts/99_utils.R")
}else{
    shim <- ""
    source("scripts/99_utils.R")
}
```

@@

dt_sites$dist <- unlist(list(unlist(st_distance(coords_ire, dt_sites)))) / 1609.34
dt_sites_close <- dt_sites[dt_sites$dist < 100,] %>%
    dplyr::arrange(dist)
head(dplyr::select(dt_sites_close, site_code, dist))

st_coordinates(dt_sites_close[1,])

>>>>

```{r, echo=FALSE}
if (dir.exists("../scripts")) {
  shim <- "../"
  source("../scripts/99_utils.R")
} else {
  shim <- ""
  source("scripts/99_utils.R")
}
```

@@

dt_sites$dist <- unlist(list(unlist(st_distance(coords_ire, dt_sites)))) / 1609.34
dt_sites_close <- dt_sites[dt_sites$dist < 100, ] %>%
  dplyr::arrange(dist)
head(dplyr::select(dt_sites_close, site_code, dist))

st_coordinates(dt_sites_close[1, ])
